\huge A Usability Evaluation of Tor Launcher

### 2016-11-11 pets2017-paper/pets2017-paper.tex
mark success p value to redo

%success rate and version
Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 0.0126$, $df = 2$, $p = 0.994$). That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

>>>>

%success rate and version
{\color {red} Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 0.0126$, $df = 2$, $p = 0.994$).} That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
